### 2015-05-10 writing/S'15 misc/newcorpus.tex
Relation handling cleanup.
Better memory management in SequenceBatch, etc.

@@

We use captions from the Flickr30k corpus \cite{hodoshimage} as the left hand side of each relation pair. That corpus ...

@@

\begin{figure}
\footnotesize
\toprule
The Stanford University NLP Group is collecting data for use in research on computer understanding of English. We appreciate your help!

We will show you the caption for a photo. We will not show you the photo. Using only the caption and what you know about the world:
\begin{itemize}
\item Write one alternate caption that is \textbf{definitely} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that \textbf{might be} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that is \textbf{definitely} a \textbf{false} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors." This is different from the maybe correct category because its impossible for the dogs to be both running and sitting.}
\end{itemize}
\textbf{Problems} (optional)   If something is wrong with the caption that makes it difficult to understand, do your best above and let us know here.
\bottomrule
\caption{\label{instructions-1}Examples of training data from the newly collected entailment corpus.}
\end{figure}

@@

% ditto examples

\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{6.5cm}cp{6.5cm}}
  \toprule
A busy street with building lined up and people walking down the street outside and nighttime. &\ii{entailment}	&People lined up\\
\rule{0pt}{3ex}Two men stand in an electric outdoor lift. &\ii{neutral}	& The two men are inspectors for the FDA, waiting to inspect the second level of the pharmaceutical plant.\\
\rule{0pt}{3ex}A young redheaded girl, wearing a yellow shirt, black pants, and sneakers, jumping in a grassy field with blue skies and wispy clouds in the background. &\ii{entailment}	& A girl jumps in a grassy field\\
\rule{0pt}{3ex}A crowd of people, one with a guitar, are standing in the street under the 7th Avenue street sign. &\ii{neutral}	& The crowd listening to the man play guitar.\\
\rule{0pt}{3ex}A woman wearing bike shorts and a skirt is riding a bike and carrying a shoulder bag.  &\ii{contradiction}& A woman driving a car.\\
    \bottomrule
  \end{tabular}
  \caption{\label{examplesofscedata}The instructions presented to workers during data collection.}
\end{table*}

@@

\begin{figure}
\footnotesize
\toprule
TODO: VALIDATION INSTRUCTIONS
\bottomrule\\

>>>>

Since our goal is to evaluate the quality of the single sentence representations in our model, we train an entailment classifier that has access only to the output of our sentence representation model, and not to any of the word or phrase representations that it used. We encourage future users of this corpus to evaluate their models in this way when possible. Our classifier is simply a stack of three 100d (NONLIN) layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the representation model itself.

@@

We use captions from the Flickr30k corpus \cite{hodoshimage} as the left hand side of each label pair. That corpus ...

@@

\begin{figure}
\footnotesize
% \toprule
The Stanford University NLP Group is collecting data for use in research on computer understanding of English. We appreciate your help!

We will show you the caption for a photo. We will not show you the photo. Using only the caption and what you know about the world:
\begin{itemize}
\item Write one alternate caption that is \textbf{definitely} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that \textbf{might be} a \textbf{true} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors."}
\item Write one alternate caption that is \textbf{definitely} a \textbf{false} description of the photo. \ii{Example: For the caption "Two dogs are running through a field." you could write "There are animals outdoors." This is different from the maybe correct category because its impossible for the dogs to be both running and sitting.}
\end{itemize}
\textbf{Problems} (optional)   If something is wrong with the caption that makes it difficult to understand, do your best above and let us know here.
% \bottomrule
\caption{\label{instructions-1}Examples of training data from the newly collected entailment corpus.}
\end{figure}

@@

% ditto examples
%
\begin{table*}
  \centering\footnotesize
  \begin{tabular}{p{6.5cm}cp{6.5cm}}
  \toprule
A busy street with building lined up and people walking down the street outside and nighttime. &\ii{entailment}	&People lined up\\
\rule{0pt}{3ex}Two men stand in an electric outdoor lift. &\ii{neutral}	& The two men are inspectors for the FDA, waiting to inspect the second level of the pharmaceutical plant.\\
\rule{0pt}{3ex}A young redheaded girl, wearing a yellow shirt, black pants, and sneakers, jumping in a grassy field with blue skies and wispy clouds in the background. &\ii{entailment}	& A girl jumps in a grassy field\\
\rule{0pt}{3ex}A crowd of people, one with a guitar, are standing in the street under the 7th Avenue street sign. &\ii{neutral}	& The crowd listening to the man play guitar.\\
\rule{0pt}{3ex}A woman wearing bike shorts and a skirt is riding a bike and carrying a shoulder bag.  &\ii{contradiction}& A woman driving a car.\\
    \bottomrule
  \end{tabular}
  \caption{\label{examplesofscedata}The instructions presented to workers during data collection.}
\end{table*}

@@

\begin{figure}
\footnotesize
%\toprule
TODO: VALIDATION INSTRUCTIONS
%\bottomrule\\
